func-descr.template

### 2025-12-15 reports/capstone-movielens.site/work/func-descr.template.Rmd
Function described: `loess_de`.
Functions described: `regularize.train_UMGYD_effect`, `regularize.train_UMGYD_effect.cv`.

```{r eval=FALSE}
cmmn_helper_func.tmpl()

@@

This function is a wrapper for the [tibble::]() function, which is called internally to modify a data frame representing the original _RMSEs Result Tibble_, which stores the _RMSE_ values for the models used in the project to predict movie ratings.

@@

```{r eval=FALSE}
umgye_rglr_helper.tmpl()

>>>>

@@

This function is a wrapper for the [tibble::]() function, which is called internally to modify a data frame object representing the original _RMSEs Result Tibble_, which stores the _RMSE_ values for the models used in the project to predict movie ratings.

@@
